`r glue::glue('Compare aggregated and non-aggregated reference: {params$library_id}')`

### 2025-07-03 analyses/cell-type-neuroblastoma-04/exploratory-notebooks/01_reference-aggregation.Rmd
file name plural

---
title: "`r glue::glue('Compare aggregated and non-aggregated reference: {params$library_id}')`"
author: "Stephanie J. Spielman"
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: true
    toc_depth: 3
    code_folding: hide
params:
  sample_id: "SCPCS000105"
  library_id: "SCPCL000122"
---

@@

aggr <- readr::read_rds(
  file.path(
    results_dir,
    params$sample_id,
    "aggregated",
    glue::glue("{params$library_id}_singler-result.rds")
  )
) |>
  as.data.frame() |>
  tibble::rownames_to_column("barcodes") |>
  dplyr::mutate(ref_type = "aggregated")

non_aggr <- readr::read_rds(
  file.path(
    results_dir,
    params$sample_id,
    "not-aggregated",
    glue::glue("{params$library_id}_singler-result.rds")
  )
) |>
  as.data.frame() |>
  tibble::rownames_to_column("barcodes") |>
  dplyr::mutate(ref_type = "non-aggregated")
```

>>>>

---
title: "`r glue::glue('Compare aggregated and non-aggregated reference: {params$library_id}')`"
author: "Stephanie J. Spielman"
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: true
    toc_depth: 3
    code_folding: hide
params:
  sample_id: "SCPCS000115"
  library_id: "SCPCL000133"
---

@@

aggr <- readr::read_rds(
  file.path(
    results_dir,
    params$sample_id,
    "aggregated",
    glue::glue("{params$library_id}_singler-results.rds")
  )
) |>
  as.data.frame() |>
  tibble::rownames_to_column("barcodes") |>
  dplyr::mutate(ref_type = "aggregated")

non_aggr <- readr::read_rds(
  file.path(
    results_dir,
    params$sample_id,
    "not-aggregated",
    glue::glue("{params$library_id}_singler-results.rds")
  )
) |>
  as.data.frame() |>
  tibble::rownames_to_column("barcodes") |>
  dplyr::mutate(ref_type = "non-aggregated")
```
